### 2019-01-29 README.Rmd
start pow methods #598
upate readme and citation

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropensci/taxize")
```

@@

@@

[afkoeppel](https://github.com/afkoeppel) - [ahhurlbert](https://github.com/ahhurlbert) - [albnd](https://github.com/albnd) - [Alectoria](https://github.com/Alectoria) - [andzandz11](https://github.com/andzandz11) - [antagomir](https://github.com/antagomir) - [arendsee](https://github.com/arendsee) - [ashenkin](https://github.com/ashenkin) - [ashiklom](https://github.com/ashiklom) - [bomeara](https://github.com/bomeara) - [bw4sz](https://github.com/bw4sz) - [cboettig](https://github.com/cboettig) - [cdeterman](https://github.com/cdeterman) - [ChrKoenig](https://github.com/ChrKoenig) - [chuckrp](https://github.com/chuckrp) - [clarson2191](https://github.com/clarson2191) - [claudenozeres](https://github.com/claudenozeres) - [cmzambranat](https://github.com/cmzambranat) - [daattali](https://github.com/daattali) - [DanielGMead](https://github.com/DanielGMead) - [davharris](https://github.com/davharris) - [davidvilanova](https://github.com/davidvilanova) - [diogoprov](https://github.com/diogoprov) - [dlebauer](https://github.com/dlebauer) - [dlenz1](https://github.com/dlenz1) - [dschlaep](https://github.com/dschlaep) - [EDiLD](https://github.com/EDiLD) - [emhart](https://github.com/emhart) - [fdschneider](https://github.com/fdschneider) - [fgabriel1891](https://github.com/fgabriel1891) - [fmichonneau](https://github.com/fmichonneau) - [gedankenstuecke](https://github.com/gedankenstuecke) - [gimoya](https://github.com/gimoya) - [GISKid](https://github.com/GISKid) - [git-og](https://github.com/git-og) - [glaroc](https://github.com/glaroc) - [gustavobio](https://github.com/gustavobio) - [ibartomeus](https://github.com/ibartomeus) - [jangorecki](https://github.com/jangorecki) - [jarioksa](https://github.com/jarioksa) - [jebyrnes](https://github.com/jebyrnes) - [johnbaums](https://github.com/johnbaums) - [jonmcalder](https://github.com/jonmcalder) - [JoStaerk](https://github.com/JoStaerk) - [jsgosnell](https://github.com/jsgosnell) - [kamapu](https://github.com/kamapu) - [karthik](https://github.com/karthik) - [katrinleinweber](https://github.com/katrinleinweber) - [KevCaz](https://github.com/KevCaz) - [kgturner](https://github.com/kgturner) - [kmeverson](https://github.com/kmeverson) - [Koalha](https://github.com/Koalha) - [ljvillanueva](https://github.com/ljvillanueva) - [Markus2015](https://github.com/Markus2015) - [mcsiple](https://github.com/mcsiple) - [MikkoVihtakari](https://github.com/MikkoVihtakari) - [millerjef](https://github.com/millerjef) - [miriamgrace](https://github.com/miriamgrace) - [mpnelsen](https://github.com/mpnelsen) - [MUSEZOOLVERT](https://github.com/MUSEZOOLVERT) - [nate-d-olson](https://github.com/nate-d-olson) - [nmatzke](https://github.com/nmatzke) - [npch](https://github.com/npch) - [paternogbc](https://github.com/paternogbc) - [philippi](https://github.com/philippi) - [pmarchand1](https://github.com/pmarchand1) - [pssguy](https://github.com/pssguy) - [RodgerG](https://github.com/RodgerG) - [rossmounce](https://github.com/rossmounce) - [sariya](https://github.com/sariya) - [scelmendorf](https://github.com/scelmendorf) - [sckott](https://github.com/sckott) - [SimonGoring](https://github.com/SimonGoring) - [snsheth](https://github.com/snsheth) - [snubian](https://github.com/snubian) - [Squiercg](https://github.com/Squiercg) - [tdjames1](https://github.com/tdjames1) - [tmkurobe](https://github.com/tmkurobe) - [tpaulson1](https://github.com/tpaulson1) - [tpoisot](https://github.com/tpoisot) - [vijaybarve](https://github.com/vijaybarve) - [wcornwell](https://github.com/wcornwell) - [willpearse](https://github.com/willpearse) - [wpetry](https://github.com/wpetry) - [zachary-foster](https://github.com/zachary-foster)

>>>>

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("ropensci/taxize")
```

@@

## Screencast

<a href="https://vimeo.com/92883063"><img src="tools/screencast.png" width="400"></a>

@@

[afkoeppel](https://github.com/afkoeppel) - [ahhurlbert](https://github.com/ahhurlbert) - [albnd](https://github.com/albnd) - [Alectoria](https://github.com/Alectoria) - [andzandz11](https://github.com/andzandz11) - [antagomir](https://github.com/antagomir) - [arendsee](https://github.com/arendsee) - [ArielGreiner](https://github.com/ArielGreiner) - [arw36](https://github.com/arw36) - [ashenkin](https://github.com/ashenkin) - [ashiklom](https://github.com/ashiklom) - [benjaminschwetz](https://github.com/benjaminschwetz) - [benmarwick](https://github.com/benmarwick) - [bomeara](https://github.com/bomeara) - [bw4sz](https://github.com/bw4sz) - [cboettig](https://github.com/cboettig) - [cdeterman](https://github.com/cdeterman) - [ChrKoenig](https://github.com/ChrKoenig) - [chuckrp](https://github.com/chuckrp) - [clarson2191](https://github.com/clarson2191) - [claudenozeres](https://github.com/claudenozeres) - [cmzambranat](https://github.com/cmzambranat) - [cparsania](https://github.com/cparsania) - [daattali](https://github.com/daattali) - [DanielGMead](https://github.com/DanielGMead) - [DarrenObbard](https://github.com/DarrenObbard) - [davharris](https://github.com/davharris) - [davidvilanova](https://github.com/davidvilanova) - [diogoprov](https://github.com/diogoprov) - [dlebauer](https://github.com/dlebauer) - [dlenz1](https://github.com/dlenz1) - [dschlaep](https://github.com/dschlaep) - [EDiLD](https://github.com/EDiLD) - [edwbaker](https://github.com/edwbaker) - [emhart](https://github.com/emhart) - [eregenyi](https://github.com/eregenyi) - [fdschneider](https://github.com/fdschneider) - [fgabriel1891](https://github.com/fgabriel1891) - [fischhoff](https://github.com/fischhoff) - [fmichonneau](https://github.com/fmichonneau) - [fozy81](https://github.com/fozy81) - [gedankenstuecke](https://github.com/gedankenstuecke) - [GISKid](https://github.com/GISKid) - [git-og](https://github.com/git-og) - [glaroc](https://github.com/glaroc) - [gpli](https://github.com/gpli) - [gustavobio](https://github.com/gustavobio) - [hlapp](https://github.com/hlapp) - [ibartomeus](https://github.com/ibartomeus) - [Ironholds](https://github.com/Ironholds) - [jangorecki](https://github.com/jangorecki) - [jarioksa](https://github.com/jarioksa) - [jebyrnes](https://github.com/jebyrnes) - [jimmyodonnell](https://github.com/jimmyodonnell) - [johnbaums](https://github.com/johnbaums) - [jonmcalder](https://github.com/jonmcalder) - [josephwb](https://github.com/josephwb) - [jsgosnell](https://github.com/jsgosnell) - [jwilk](https://github.com/jwilk) - [kamapu](https://github.com/kamapu) - [karthik](https://github.com/karthik) - [katrinleinweber](https://github.com/katrinleinweber) - [KevCaz](https://github.com/KevCaz) - [kgturner](https://github.com/kgturner) - [kmeverson](https://github.com/kmeverson) - [Koalha](https://github.com/Koalha) - [ljvillanueva](https://github.com/ljvillanueva) - [maelle](https://github.com/maelle) - [Markus2015](https://github.com/Markus2015) - [mcsiple](https://github.com/mcsiple) - [MikkoVihtakari](https://github.com/MikkoVihtakari) - [millerjef](https://github.com/millerjef) - [miriamgrace](https://github.com/miriamgrace) - [MK212](https://github.com/MK212) - [mpnelsen](https://github.com/mpnelsen) - [MUSEZOOLVERT](https://github.com/MUSEZOOLVERT) - [nate-d-olson](https://github.com/nate-d-olson) - [nmatzke](https://github.com/nmatzke) - [npch](https://github.com/npch) - [paternogbc](https://github.com/paternogbc) - [patperu](https://github.com/patperu) - [pederengelstad](https://github.com/pederengelstad) - [philippi](https://github.com/philippi) - [pmarchand1](https://github.com/pmarchand1) - [PrincessPi314](https://github.com/PrincessPi314) - [pssguy](https://github.com/pssguy) - [raredd](https://github.com/raredd) - [rec3141](https://github.com/rec3141) - [Rekyt](https://github.com/Rekyt) - [RodgerG](https://github.com/RodgerG) - [rossmounce](https://github.com/rossmounce) - [sariya](https://github.com/sariya) - [scelmendorf](https://github.com/scelmendorf) - [sckott](https://github.com/sckott) - [SimonGoring](https://github.com/SimonGoring) - [snsheth](https://github.com/snsheth) - [snubian](https://github.com/snubian) - [Squiercg](https://github.com/Squiercg) - [taddallas](https://github.com/taddallas) - [tdjames1](https://github.com/tdjames1) - [tmkurobe](https://github.com/tmkurobe) - [toczydlowski](https://github.com/toczydlowski) - [tpaulson1](https://github.com/tpaulson1) - [tpoisot](https://github.com/tpoisot) - [vijaybarve](https://github.com/vijaybarve) - [wcornwell](https://github.com/wcornwell) - [willpearse](https://github.com/willpearse) - [wpetry](https://github.com/wpetry) - [yhg926](https://github.com/yhg926) - [zachary-foster](https://github.com/zachary-foster)
